Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-30 ms.tex
fixing things (e.g. table)

   10$^{7}$ & ... & 50 & 0.38 & $ 2.0 \times 10^{ -4 }$ & 4.5 & 0.2, 0.6\\

@@

$    10^{ 6 }$ & 600 & 25 & $ 9.4 \times 10^{ -2 }$ & $ 7.4 \times 10^{ -6 }$ & $ 1.1 \times 10^{ 2 }$ \\

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{cooling.eps}
  \caption{\label{fig:cooling} Ratio of the rates of heating to
radiative cooling, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$, as a
function of radius (solid lines) for each of our solutions shown in
Figure \ref{fig:profiles}.  Dashed lines show the ratio
of the cooling timescale to the free-fall timescale $t_{\rm cool}/t_{\rm ff}$.
For high heating rates both ratios are approximately equal at the
stagnation radius (squares).  When $\dot{q}_{\rm
heat}/\dot{q}_{\rm rad} \lesssim 10$ (or, equivalently, $t_{\rm cool}/t_{\rm ff}
\lesssim 10$ near the stagnation radius), then the flow is susceptible to thermal instabilities.}
\end{figure}

Fig.~\ref{fig:cooling} shows the ratio of wind heating to radiative
cooling, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$
(eq.~[\ref{eq:cooling2}] and surrounding discussion) as a function of
radius for our fiducial solutions shown in Figure \ref{fig:profiles}.
Radiative cooling is calculated using the cooling function of \citet{Draine:2011a} for solar metallicity.  For high heating rates of $v_{w} = 600$ and
$1200$ km s$^{-1}$ cooling is unimportant across all radii, while for
$v_{w} = 300$ km s$^{-1}$ we see that $\dot{q}_{\rm
  heat}/|\dot{q}_{\rm rad}|$ and $\tcool/\tff$ can be less than unity,
depending on the wind mass loss parameter $\eta$.  Because at the
stagnation radius $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ reaches
within a factor of two of its minimum across the entire grid, the
value of $(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)_{r_{s}}$ can be
taken as diagnostic of thermal instability at all radii.

@@

Although most of our solutions neglect thermal conduction and
radiative cooling, these effects are explore explicitly in subset of simulations, as marked by dagger symbols in Table \ref{table:models}.  For cases which are far from being thermally
unstable when cooling is neglected (e.g., $M_{\bullet} =
10^{8}M_{\odot}$, $v_{w} = 600$ km s$^{-1}$, $r_{b} = 100$ pc, $\eta =
0.2$, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| = 76$), including radiative cooling has little effect on the key properties of the solution, such as the stagnation radius, mass accretion rate, and the cooling ratio $\dot{q}_{\rm
  heat}/|\dot{q}_{\rm rad}|$.  However, for solutions that are marginally thermally stable, including radiative losses acts to significantly decrease $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$.  We calculated solutions with radiative
cooling for all cusp galaxies with $v_w=300$ km s$^{-1}$ and for all
core galaxies with $v_w=600 $ km s$^{-1}$, each for three different
values of $\eta = 0.02, 0.2, 0.6$, spanning the physical range of
expected mass loss for continuous star formation (Fig.~\ref{fig:vwSources}).  Solutions found to be unstable for all values of $\eta$ are marked in boldface as ``TI" in Table
\ref{table:models}, with the unstable values of $\eta$ provided in the final column.

>>>>

   10$^{7}$ & 300 & 50 & 0.38 & $ 2.0 \times 10^{ -4 }$ & 4.5 & 0.2, 0.6\\

@@

$    10^{ 6 }$ & 600 & 25 & $ 9.4 \times 10^{ -2 }$ & $ 7.4 \times
10^{ -6 }$ & $ 1.1 \times 10^{ 2 }$ & 0.2, 0.6\\

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{cooling.eps}
  \caption{\label{fig:cooling} Ratio of the rates of heating to
    radiative cooling, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$, as a
    function of radius (solid lines) for a $\Mbh=10^7 \Msun$ cusp
    galaxy ($\Gamma=0.8$).  Dashed lines show the ratio of the cooling
    timescale to the free-fall timescale $t_{\rm cool}/t_{\rm ff}$.
    For high heating rates both ratios are approximately equal at the
    stagnation radius (squares).  When $\dot{q}_{\rm
      heat}/\dot{q}_{\rm rad} \lesssim 10$ (or, equivalently, $t_{\rm
      cool}/t_{\rm ff} \lesssim 10$ near the stagnation radius), then
    the flow is susceptible to thermal instabilities.}
\end{figure}

Fig.~\ref{fig:cooling} shows the ratio of wind heating to radiative
cooling, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$
(eq.~[\ref{eq:cooling2}] and surrounding discussion) as a function of
radius for $v_w=300, 600,$ and 1200 km/s, $\Mbh=10^{7} \Msun$, and
$\Gamma=0.8$.  Radiative cooling is calculated using the cooling
function of \citet{Draine:2011a} for solar metallicity.  For high
heating rates of $v_{w} = 600$ and $1200$ km s$^{-1}$ cooling is
unimportant across all radii, while for $v_{w} = 300$ km s$^{-1}$ we
see that $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ and $\tcool/\tff$
can be less than unity, depending on the wind mass loss parameter
$\eta$.  Because at the stagnation radius $\dot{q}_{\rm
  heat}/|\dot{q}_{\rm rad}|$ reaches within a factor of two of its
minimum across the entire grid, the value of $(\dot{q}_{\rm
  heat}/|\dot{q}_{\rm rad}|)_{r_{s}}$ can be taken as diagnostic of
thermal instability at all radii.

@@

Although most of our solutions neglect thermal conduction and
radiative cooling, these effects are explored explicitly in subset of
simulations.  Dagger symbols in Table \ref{table:models} correspond to
solutions for which we turned on radiative cooling.  For cases which
are far from being thermally unstable when cooling is neglected (e.g.,
$M_{\bullet} = 10^{8}M_{\odot}$, $v_{w} = 600$ km s$^{-1}$, $r_{b} =
100$ pc, $\eta = 0.2$, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| = 76$),
including radiative cooling has little effect on the key properties of
the solution, such as the stagnation radius, mass accretion rate, and
the cooling ratio $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$.  However,
for solutions that are marginally thermally stable, including
radiative losses acts to significantly decrease $\dot{q}_{\rm
  heat}/|\dot{q}_{\rm rad}|$.  We calculated solutions with radiative
cooling for all cusp galaxies with $v_w=300$ km s$^{-1}$ and for all
core galaxies with $v_w=600 $ km s$^{-1}$, each for three different
values of $\eta = 0.02, 0.2, 0.6$, spanning the physical range of
expected mass loss for continuous star formation
(Fig.~\ref{fig:vwSources}).  Solutions found to be unstable for all
values of $\eta$ are marked in boldface as ``TI" in Table
\ref{table:models}, with the unstable values of $\eta$ provided in the
final column.
